---
title: "CFR-fitting"
output: html_document
---

##The pandemic worldwide is still continues. To see the trend of the COVID-19 all over the world, we can use the data from WHO to show the daily confirmed cases and daily confirmed deaths.  
Firstly, download the data from WHO and read it into R
```{r}
#setwd("C:\\Users\\Laplace\\Documents\\R work in CityU\\SIR epidemics")
mydata <- read.csv("WHO-COVID-19-global-data.csv", sep = ",")
names(mydata)[1] <- "Date_reported"
mydata$Date_reported <- as.Date(as.character(mydata$Date_reported), format = "%Y/%m/%d")
```

##Define the daily reported cases and daily deaths
```{r}
library(dplyr)
daily_reported_cases <- mydata %>% 
  filter(Date_reported >= as.Date("20200201", format = "%Y%m%d")) %>%
  group_by(Date_reported) %>% 
  summarise(daily_new_cases = sum(New_cases))

daily_death_cases <- mydata %>% 
  filter(Date_reported >= as.Date("20200201", format = "%Y%m%d")) %>%
  group_by(Date_reported) %>% 
  summarise(daily_death_cases = sum(New_deaths))
```
##Show the daily number of reported cases and daily number of reported deaths worldwide

```{r}
library(ggplot2)
datebreaks <- seq(as.Date("2020-02-01"), as.Date("2021-03-31"),by = "15 day")
ggplot(data = daily_reported_cases, aes(x = Date_reported, y = daily_new_cases)) +
  geom_point()+
  geom_smooth()+
  scale_x_date(breaks = datebreaks) + 
  theme(axis.text.x = element_text(angle = 30, hjust = 1))+
  labs(x = "Date",y = "Reported cases",title = "Daily number of reported cases worldwide (from 2020-02-01 to 2021-03-31)") 
 
ggplot(data = daily_death_cases, aes(x = Date_reported, y = daily_death_cases)) +
  geom_point()+
  geom_smooth()+
  scale_x_date(breaks = datebreaks) + 
  theme(axis.text.x = element_text(angle = 30, hjust = 1))+
  labs(x = "Date",y = "Death cases",title = "Daily number of reported deaths worldwide (from 2020-02-01 to 2021-03-31)") 
```
##Calculate the case fatality rate without any type of delay

```{r}
CFR_without_delay <- data.frame(Date_reported = daily_death_cases$Date_reported, CFR = daily_death_cases$daily_death_cases/daily_reported_cases$daily_new_cases)

```
##Show the trend of CFR
```{r}
ggplot(data = CFR_without_delay, aes(x = Date_reported, y = CFR)) +
  geom_point()+
  geom_smooth(method = "gam")+
  scale_x_date(breaks = datebreaks) + 
  theme(axis.text.x = element_text(angle = 30, hjust = 1))+
  labs(x = "Date",y = "Cumulative Fatality Rate(CFR)",title = "Daily number of CFR(without delay) worldwide (from 2020-02-01 to 2021-03-31)") 
```

